---
title: "R Notebook Narcissism"
output: html_notebook
---


```{r setup, message=FALSE, warning=FALSE}
library(ggplot2)
library(dplyr)
library(psych)

```
Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
```{r}
  df <- read.csv("data.csv", stringsAsFactors = FALSE)
  #df
```
## Inspection of the data and checking for missing values
```{r  setup, message=FALSE, warning=FALSE}
str(df)       # Data structure
summary(df)   # Summary of each column
head(df)      # First few rows
colSums(is.na(df))  # Count missing values in each column
```
We have concluded there are no missing values in the data

## Detecting outliers
```{r}

```

## Visualizing Key Trends
```{r}
df_gender_1 <-df[df$gender == 1, ] 
nrow(df_gender_1)
nrow(df_gender_2)
df_gender_2 <-df[df$gender == 2, ] 
df_min_narcissistic <- df[df[, 1] == 0, ]  
nrow(df_min_narcissistic)
df_min_narcissistic_1 <- df_min_narcissistic[df_min_narcissistic$gender == 1, ] 
nrow(df_min_narcissistic_1)  

```
The number of gender 1 (Assuming men) who took the test is: 6425
The number of gender 2 (Assuming women) who took the test is: 4766
The number of people who scored 0 on the NPI-40 is 84.
The number of men is (Assuming men is 1): 47
The number of women is(Assuming women is 2): 37