---
title: "R Notebook Narcissism"
output: html_notebook
author: "Elena Spirova"
---

```{r}
rmarkdown::render("~/Documents/workspace/1va god master/seminar data science narcissism/narcissism_analysis.Rmd")
```



```{r, message=FALSE, warning=FALSE}
library(ggplot2)
library(dplyr)
library(psych)
library(corrplot)

```


```{r}
  df <- read.csv("data.csv", stringsAsFactors = FALSE)
  nrow(df)
```
## Inspection of the data and checking for missing values
```{r message=FALSE, warning=FALSE, include=FALSE}
str(df)       # Data structure
summary(df)   # Summary of each column
head(df)      # First few rows
colSums(is.na(df))  # Count missing values in each column
```
We have concluded there are no missing values in the data


## Taking care of missing values
From the Kaagle dataset everything seems fine except the gender column since
they other than 1=male and 2=female, we have 0=did not input a value and
3=other. Since in our research we are interested in knowing the differences in 
narcissistic traits between men and women we will omit the rows with the other
two options.
```{r}
df <- df[df$gender %in% c(1, 2), ]
nrow(df)
```
Result 11243 - 11191 = 52 rows were omitted.


## Visualizing Key Trends
```{r}
df_gender_1 <-df[df$gender == 1, ] 
nrow(df_gender_1)

df_gender_2 <-df[df$gender == 2, ] 
nrow(df_gender_2)

df_min_narcissistic <- df[df[, 1] == 0, ]  
nrow(df_min_narcissistic)

df_min_narcissistic_1 <- df_min_narcissistic[df_min_narcissistic$gender == 1, ] 
nrow(df_min_narcissistic_1)  

```
The number of gender 1 (Assuming men) who took the test is: 6425
The number of gender 2 (Assuming women) who took the test is: 4766
The number of people who scored 0 on the NPI-40 is 84.
The number of men who scored 0 is: 47
The number of women who scored 0 is: 37


## Subscales
ðŸ“Œ Leadership/Authority
Items:
1, 5, 10, 11, 12, 27, 32, 33, 34, 36, 40

ðŸ“Œ Grandiose Exhibitionism
Items:
4, 7, 15, 19, 20, 26, 28, 30, 38, 39

ðŸ“Œ Entitlement/Exploitativeness
Items:
3, 14, 17, 24


```{r}
df$authority_score <- rowSums(df[, c("Q1", "Q5", "Q10", "Q11", "Q27", "Q32",
                                     "Q33", "Q34", "Q36", "Q40")])
df$exibitionism_score <- rowSums(df[, c("Q4", "Q7", "Q15", "Q19", "Q20", "Q26",
                                       "Q28", "Q30", "Q38", "Q39")])
df$entitlement_score <- rowSums(df[, c("Q3", "Q14", "Q17", "Q24")])
```



```{r}
# Summarize mean scores
df_summary <- df %>%
  group_by(gender) %>%
  summarise(
    authority = mean(authority_score),
    entitlement = mean(entitlement_score),
    exibitionism = mean(exibitionism_score)
  )

print(df_summary)

# Visualize gender differences
ggplot(df_summary, aes(x = factor(gender), y = authority)) +
  geom_col(fill = "skyblue") +
  labs(title = "Authority by Gender", x = "Gender", y = "Mean Score")

# Visualize gender differences
ggplot(df_summary, aes(x = factor(gender), y = entitlement)) +
  geom_col(fill = "green") +
  labs(title = "Entitlement by Gender", x = "Gender", y = "Mean Score")

# Visualize gender differences
ggplot(df_summary, aes(x = factor(gender), y = exibitionism)) +
  geom_col(fill = "red") +
  labs(title = "Exibitionism by Gender", x = "Gender", y = "Mean Score")

```

## Finding correlations 

### ðŸ”„ 1. Correlation Matrix Between Subscales
```{r}
# Select only subscale scores
subscale_data <- df[, c("authority_score", 
                        "exibitionism_score", 
                        "entitlement_score")]

# Compute correlation matrix
cor_matrix <- cor(subscale_data)

# Visualize
corrplot(cor_matrix, method = "circle",
         type = "upper", 
         tl.col = "black", tl.srt = 45)

```
### ðŸ” 2. Correlation Matrix by Gender

```{r}
cor_male <- cor(df[df$gender == 1, c("authority_score", 
                                     "exibitionism_score",
                                     "entitlement_score")])
cor_female <- cor(df[df$gender == 2, c("authority_score",
                                       "exibitionism_score",
                                       "entitlement_score")])

# Plot both
corrplot(cor_male, method = "number", title = "Males", mar = c(0,0,1,0))
corrplot(cor_female, method = "number", title = "Females", mar = c(0,0,1,0))

```
```{r}
library(tidyr)

df_long <- df %>%
  pivot_longer(cols = c(authority_score, entitlement_score, exibitionism_score),
               names_to = "subscale",
               values_to = "sc")
df_long
ggplot(df_long, aes(x = factor(gender), y = sc, fill = factor(gender))) +
  geom_boxplot() +
  facet_wrap(~ subscale, scales = "free_y") +
  labs(title = "Distribution of Subscale Scores by Gender", 
       x = "Gender",
       y = "Score") +
  scale_fill_manual(values = c("skyblue", "pink"), labels = c("Male", "Female"))

```